### 2021-04-13 ch05_paper_ecs/paper_ecs.tex
Fixed list of figures

This work is already published in \textcite{Schlund2020a}. For this paper, the
author of this thesis led the writing and the analysis and implemented the code
to reproduce this study with all figures and tables using the \ac{ESMValTool}.
In this \lcnamecref{ch:05:paper_ecs}, we first introduce the data (climate
model output and observations) and methods used in this study
(\cref{sec:05:data_and_methods}). After that, we present the 11 emergent
constraints on \acs{ECS} and evaluate them on the \acs{CMIP}5 and \acs{CMIP}6
ensemble (\cref{sec:05:comparison_of_emergent_constraints}). Finally, we
provide a discussion (\cref{sec:05:discussion}) and a summary of the results
(\cref{sec:05:summary}).

@@

\begin{figure}[p]
  \centering
  \begin{subfigure}[b]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/scatterplot_merged_training_data_bri.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:a}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/target_distribution_training_data_bri.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:b}
  \end{subfigure}
  \\
  \begin{subfigure}[b]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/scatterplot_merged_training_data_cox.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:c}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/target_distribution_training_data_cox.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:d}
  \end{subfigure}
  \\
  \begin{subfigure}[b]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/scatterplot_merged_training_data_lip.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:e}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/target_distribution_training_data_lip.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:f}
  \end{subfigure}
  \caption[
    Emergent constraints BRI, COX, and LIP applied to the \acs{CMIP}5 and
    \acs{CMIP}6 ensemble.
  ]{
    Emergent constraints BRI, COX, and LIP applied to the \acs{CMIP}5 (blue)
    and \acs{CMIP}6 ensemble (orange). (a), (c), (e) Emergent relationships
    (solid lines) for the \acs{CMIP} models (numbers; see
    \cref{tab:app:a:cmip5_emergent_constraints_part1,%
      tab:app:a:cmip6_emergent_constraints_part1} for details) with their
    \aclp{SPE} (blue and orange shaded areas; see \cref{eq:02:spe}). The
    vertical dashed line corresponds to the observational reference with its
    standard error (gray shaded area). The horizontal dashed lines show the
    best estimates of the constrained \acf{ECS}, and the colored points mark
    the \aclp{MMM} for \acs{CMIP}5 (blue) and \acs{CMIP}6 (orange). (b), (d),
    (f) \Aclp{PDF} for \acs{ECS} of the emergent constraints (solid lines;
    see \cref{eq:02:pdf_y_given_x0}) and the unconstrained model ensembles
    (histograms). Due to the availability of data, the histograms may differ
    for the different emergent constraints. \AdaptedFrom{Schlund2020a}.
  }
  \label{fig:05:bri_cox_lip}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch05_paper_ecs/figs/constrained_ranges_summary.pdf}
  \caption[
    Overview of the constrained \acf{ECS} ranges given by the 11 emergent
    constraints using the \acs{CMIP}5 and \acs{CMIP}6 ensemble.
  ]{
    Overview of the constrained \acf{ECS} ranges given by the 11 analyzed
    emergent constraints using the \acs{CMIP}5 (blue) and \acs{CMIP}6 (orange)
    ensemble. The bars correspond to the $66 \unit{\%}$ confidence intervals
    ($\rangeunit{17}{83}{\%}$) calculated from the constrained \acl{PDF} of
    \acs{ECS} following \cref{eq:02:pdf_y_given_x0}. The vertical black lines
    illustrate the corresponding best estimates of the distributions. For
    almost all emergent constraints, the constrained best estimate and range of
    \acs{ECS} are higher in the \acs{CMIP}6 ensemble.
  }
  \label{fig:05:overview_results}
\end{figure}

>>>>

This work is already published in \textcite{Schlund2020a}. For this paper, the
author of this thesis led the writing and the analysis and implemented the code
to reproduce this study with all figures and tables using the \ac{ESMValTool}.
In this \lcnamecref{ch:05:paper_ecs}, we first introduce the data (climate
model output and observations) and methods used in this study
(\cref{sec:05:data_and_methods}). After that, we present the 11 emergent
constraints on \acs{ECS} and evaluate them on the \acs{CMIP}5 and \acs{CMIP}6
ensembles (\cref{sec:05:comparison_of_emergent_constraints}). Finally, we
provide a discussion (\cref{sec:05:discussion}) and a summary of the results
(\cref{sec:05:summary}).

@@

\begin{figure}[p]
  \centering
  \begin{subfigure}[b]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/scatterplot_merged_training_data_bri.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:a}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/target_distribution_training_data_bri.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:b}
  \end{subfigure}
  \\
  \begin{subfigure}[b]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/scatterplot_merged_training_data_cox.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:c}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/target_distribution_training_data_cox.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:d}
  \end{subfigure}
  \\
  \begin{subfigure}[b]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/scatterplot_merged_training_data_lip.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:e}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch05_paper_ecs/figs/target_distribution_training_data_lip.pdf}
    \caption{}
    \label{fig:05:bri_cox_lip:f}
  \end{subfigure}
  \caption[
    Emergent constraints BRI, COX, and LIP applied to the \acs{CMIP}5 and
    \acs{CMIP}6 ensembles.
  ]{
    Emergent constraints BRI, COX, and LIP applied to the \acs{CMIP}5 (blue)
    and \acs{CMIP}6 ensembles (orange). (a), (c), (e) Emergent relationships
    (solid lines) for the \acs{CMIP} models (numbers; see
    \cref{tab:app:a:cmip5_emergent_constraints_part1,%
      tab:app:a:cmip6_emergent_constraints_part1} for details) with their
    \aclp{SPE} (blue and orange shaded areas; see \cref{eq:02:spe}). The
    vertical dashed line corresponds to the observational reference with its
    standard error (gray shaded area). The horizontal dashed lines show the
    best estimates of the constrained \acf{ECS}, and the colored points mark
    the \aclp{MMM} for \acs{CMIP}5 (blue) and \acs{CMIP}6 (orange). (b), (d),
    (f) \Aclp{PDF} for \acs{ECS} of the emergent constraints (solid lines;
    see \cref{eq:02:pdf_y_given_x0}) and the unconstrained model ensembles
    (histograms). Due to the availability of data, the histograms may differ
    for the different emergent constraints. \AdaptedFrom{Schlund2020a}.
  }
  \label{fig:05:bri_cox_lip}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch05_paper_ecs/figs/constrained_ranges_summary.pdf}
  \caption[
    Overview of the constrained \acf{ECS} ranges given by the 11 emergent
    constraints using the \acs{CMIP}5 and \acs{CMIP}6 ensembles.
  ]{
    Overview of the constrained \acf{ECS} ranges given by the 11 analyzed
    emergent constraints using the \acs{CMIP}5 (blue) and \acs{CMIP}6 (orange)
    ensembles. The bars correspond to the $66 \unit{\%}$ confidence intervals
    ($\rangeunit{17}{83}{\%}$) calculated from the constrained \acl{PDF} of
    \acs{ECS} following \cref{eq:02:pdf_y_given_x0}. The vertical black lines
    illustrate the corresponding best estimates of the distributions. For
    almost all emergent constraints, the constrained best estimate and range of
    \acs{ECS} are higher in the \acs{CMIP}6 ensemble.
  }
  \label{fig:05:overview_results}
\end{figure}
